SDSS-IV MaNGA: Radial Profiles of Specific Star Formation Rate in Nearby Interacting Galaxies

### 2020-07-15 maintex.tex
next draft

\begin{abstract}
We study the spatial profile of the star formation rate (SFR) in a sample of 202 interacting galaxies within the MaNGA (Mapping Nearby Galaxies at Apache Point Observatory) survey. We find that the specific star formation rate (sSFR) is centrally enhanced in interacting galaxies by $\sim$0.25 $\pm$ 0.1 but that there is no enhancement or suppression in their disks. We further investigate how these profiles behave as a function of their stellar mass, mass ratio, and projected separation. We find that the sSFR profiles are unaffected by the stellar masses of the interacting galaxies; however, they are affected by the mass ratio between the galaxies where the galaxies with the smallest mass ratios feature the largest enhancement to their sSFR. We also find that, in pairs with large mass ratios ($|\Delta$log(M)$|$ $=$ 0.5 $-$ 1.5), the less massive galaxy of the pair has slightly higher levels of sSFR enhancement, $\sim$0.1 dex, than the more massive galaxies in the pair. We also find that the level of sSFR enhancement increases with closer projected separations; however, the closest pairs, $\le$5 kpc, show no signs of sSFR enhancement/suppression. We suspect that these close pairs are merging galaxies which have passed their first pericenter, but the merger induced gas-inflows have yet to reach the centers of these galaxies. We make a simple model for the future mass growth of the galaxies due to the merger induced star formation. We predict that the paired galaxies in our sample will see a mass growth rate in their centers which is 1.6$-$2.3$\times$ higher than secular mass growth, showing that the merger induced star formation can significantly alter the stellar mass distribution. 
\end{abstract}

\keywords{galaxies: active --- galaxies: nuclei --- galaxies: interactions}

@@

% Organization
This paper is organized as follows; in Section \ref{sec:data} we will discuss the properties of the MaNGA survey along with the photometric catalogs which we use characterize the stellar masses and geometries or our galaxies, in Section \ref{sec:analysis} we will discuss how we extract emission lines from the MaNGA survey and how we calculate star formation rates from them, in Section \ref{sec:pair} we discuss the construction of our pair samples, in Section \ref{sec:control} we discuss the construction of a sample of isolated, control galaxies, in Section \ref{sec:radial} we build the radial profiles for both the paired and control galaxies, in Section \ref{sec:results} we discuss the results of the constructed radial profiles, and in Section \ref{sec:sum} we discuss and summarize the finding of the work.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Data}\label{sec:data}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering
\includegraphics[width=\linewidth]{fig/Mi-z.pdf}
\caption[]{\textbf{Left:} The luminosity $-$ redshift distribution of the three MaNGA subsamples; The Primary Sample (blue), the Secondary Sample (red) and the Color-Enhanced Sample (green). \textbf{Right:} The stellar mass $-$ redshift distribution of the three samples. }
\label{fig:Mi-z}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

MaNGA is an a IFS survey based at Apache Point Observatory (APO) which used the SDSS (Sloan Digital Sky Survey) 2.5-meter telescope along with two dual-channel BOSS spectrographs. MaNGA captures spectra through 17 integral field units (IFUs) with variable numbers of fibers; 19, 37, 61, 91, and 127 fibers covering 12.5\arcsec, 17.5\arcsec, 22.5\arcsec, 27.5\arcsec, and 32.5\arcsec on the sky respectively. MaNGA is an optical survey with a spectral coverage of 3600$-$10,300 \AA\ with a resolution of R $\sim$ 2000 and a median spectra coverage of 2.5\arcsec\ FWHM \citep{Bundy:2015}.

MaNGA targets galaxies from a subset of 41,154 galaxies from the NASA-Sloan Atlas (NSA) with a redshift range of 0.01 $<$ z $<$ 0.15 and a luminosity range of -17.7 $<$ $\mathcal{M_{\rm i}}$ $<$ -24.0, where $\mathcal{M_{\rm i}}$ is the rest frame i-band magnitude within the survey's elliptical Petrosian apertures. MaNGA plans to cover 10,000 galaxies with a flat stellar mass distribution at two spatial coverages, 1.5 \reff\ and 2.5 \reff\ (where \reff\ is the radius which contains 50\% of the galaxy's total light). In this work we use the data from the internal data release, MPL-8, which covers 6142 unique galaxies.

The MaNGA sample is split into three subsamples; the Primary Sample, Secondary Sample, and Color-Enhanced Sample. The Primary sample contains the galaxies which are covered out to 1.5 \reff\ and makes up 47\% of the survey. The Secondary contains the galaxies which are covered out to 2.5 \reff\ and makes up 37\% of the survey. The Color-Enhanced sample is designed to select rarer galaxy types with a spatial coverage of 2.5 \reff\ and makes up 16\% of the survey.

Because of the survey's flat stellar mass distribution and uniform spatial coverage, these samples have a unique ``banana" shaped distribution in redshift and luminosity, seen in Figure \ref{fig:Mi-z}. Because the Secondary and Color-Enhanced samples use a wider spatial coverage than the Primary sample, the Secondary and Color-Enhanced Samples will posses galaxies of higher redshifts than galaxies at the same stellar masses in the Primary sample. This distribution will be important later when we match control galaxies to paired galaxies based on their stellar masses and redshifts.

%%% NSA and Simard+11
We use photometric data from the NSA catalog and \citet{Simard:2011} (from now on \simard). We use the r-band elliptical Petrosian apertures from the NSA catalog and the r-band elliptical S\'ersic apertures from \simard\ to characterize the geometry of galaxies with pairs identified outside of the IFU (the outside-IFU sample) and galaxies identified within the IFU (the inside-IFU sample) respectively. We further use the total stellar masses extracted from these apertures to quantify the total stellar masses of the galaxies, the NSA catalog contains its own calculation for stellar mass and we use the stellar mass calculation from \citet{Mendel:2014} for the \simard\ apertures.

We use two different photometric catalogs here because the NSA catalog covers the entirety of the MaNGA sample, but does not adequately fit the geometry of galaxies with close companions. In many of the cases where we have a MaNGA target with an inside-IFU pair, the NSA catalog's algorithm fails to model the geometry of the MANGA target as the algorithm fails to separately deblend the two galaxies. We found that the algorithm used in the \simard\ catalog models the galaxies with close companions much better; however, the catalog does not completely cover our sample. We use both of the catalogs as a compromise to maintain the sample size in the outside-IFU sample, where the NSA catalog models the paired galaxies' geometry well, and to obtain better geometry in our inside-IFU sample, which is poorly fitted by the NSA catalog's algorithm.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Analysis}\label{sec:analysis}
\subsection{Emission Lines}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=\linewidth]{fig/bpt-cmd.pdf}
\caption[]{\textbf{Left:} Color-magnitude diagram for MaNGA galaxies ({\it colored circles}). The color of the symbol reflects the local density around each data point in this color-magnitude plane, as indicated by the color bar on the top. The MaNGA galaxies with close companions are marked with {\it grey diamonds}. From top to bottom, the dashed lines divide the sample into red sequence, green valley, and blue cloud. The star-forming galaxy sample used in this paper are the galaxies below the lower dividing line. \textbf{Right:} The 2-D histogram showing the BPT classification \citep{Baldwin:1981} of individual spaxels within our star-forming control and pair samples. The color of each bin represents the number density of spaxels, normalized to one. The solid black line represents the theoretically determined maximum starburst line of \citet{Kewley:2001} and the dashed black line is the analytical \citet{Kauffmann:2003} line. This shows the capability of the CMD to select star-forming galaxies as most of the spaxels within the selected galaxies fall beneath the starburst line.}
\label{fig:cmd}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%% Reddening
We correct the emission lines for reddening using the extinction curve from \citet{Cardelli:1989} with updated coefficients from \citet{ODonnell:1994}. The extinction in parameterized as R$_V$ $\equiv$ A$_V$/E(B$-$V) $=$ 3.1, where we estimate the value of the V-band extinction, A$_V$, by comparing the H$\alpha$/H$\beta$ ratio to the expected value of 2.85 for case-B recombination. We apply the extinction correction to all of the extracted emission lines.

\subsection{Star Formation Rates}
To ensure that the observed emission lines are created by HII regions, we classify galaxies as star forming using both the color-magnitude diagram (CMD) and the BPT diagram \citep{Baldwin:1981}. We show the CMD in Figure \ref{fig:cmd} along with demarcation lines which separate the blue cloud, red sequence, and green valley. We established the demarcation lines by collapsing the CMD to a color histogram for each of the three regions. We then varied the slopes between the regions until we found the slopes which best fit the data. These demarcation lines are;

@@

The BPT diagnostic uses emission line ratios to separate ionization sources; star formation and active galactic nuclei (AGN). The two ionization sources are often separated by either the theoretical maximum starburst line from \citet{Kewley:2001} or the analytically fitted line from \citet{Kauffmann:2003}, given below in Equations \ref{eq:kewley} and \ref{eq:kauffmann} respectively.

Where \OIII$\lambda$5007, H$\beta$, \NII$\lambda$6584, and H$\alpha$ are emission line fluxes extracted from the MaNGA spectra within the inner 2 arcseconds of the galaxies. It has also been shown that hot low mass evolved stars (HOLMES) in retired galaxies can mimic HII regions and AGN on the BPT diagram \citep{Stasinska:2008}. We apply an H$\alpha$ equivalent width (EW) cut of \ewha\ $>$ 3\AA\ to remove these retired galaxies \citet{Cid-Fernandes:2011}. In this work, we define star forming galaxies as those which are in the blue cloud in the CMD and which are below the theoretical maximum starburst line from \citet{Kewley:2001} on the BPT diagram.

@@

Since the stellar mass of a galaxy is not uniformly distributed within the galaxy, we normalize the SFR by the local stellar mass, giving us the specific star formation rate (sSFR). The local stellar masses used here is the stellar mass calculated by {\sc SPFIT}'s fit to the stellar continuum with each spaxel.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Pair Sample}\label{sec:pair}
We build two different pair samples in this work; the inside-IFU sample which contains paired galaxies where both galaxies are contained within a single MaNGA IFU and the outside-IFU sample where a MaNGA target galaxies is coupled with another galaxies found outside of the MaNGA IFU.

\subsection{Inside-IFU Sample}\label{sec:inside}
In our previous work, \citet{Fu:2018}, we showed that $\sim$5.7\% of the MaNGA observations have at least one companion galaxy within the field of view of the IFU. In this work we use a refined pair identification process which is also expanded for the most recent internal data release, MPL-8.

We use SDSS photometric objects to create a catalog of objects within the fields of view of the MaNGA IFUs. We extract their spectra from the MaNGA datacubes through a 1\arcsec\ aperture and fit the spectra with {\sc SPFIT} assuming the MaNGA target's redshift. The spectra is then sorted into different categories; ``good" galaxy spectra, broad-line AGN, foreground star, foreground/background galaxies, or poor S/N objects. The ``good" galaxy spectra are the objects whose spectra is well modeled by {\sc SPFIT} at the target galaxy's redshift, whether it is the target galaxy itself or a nearby companion galaxy. This means that the companion galaxy can be within $\pm$3000 km s$^{-1}$ of the MaNGA target. We found 6573 ``good" objects, 57 broad-line AGN, 836 foreground stars, 319 foreground/background galaxies, and 1546 objects with poor S/N.

From the 6573 galaxies with good spectra, 404 of the MaNGA IFUs have multiple objects within the IFU. We further restrict the sample by setting a relative velocity cut of $\Delta$v $<$ 500 km s$^{-1}$ to remove projected companions and we also require that the galaxies are classified as star forming as described in Section \ref{sec:analysis}. These requirements reduce our sample down to 124 star forming galaxies (SFGs).

We characterize the geometry of the inside-IFU galaxies with the r-band elliptical S\'ersic apertures and we characterize the total stellar mass of the galaxies with the stellar masses from \citet{Mendel:2014}. The Simard+11 and \citet{Mendel:2014} catalogs do not completely cover the MaNGA sample. Out of the 124 SFGs in the inside-IFU sample, 41 of the SFGs are covered by both \simard\ and \citet{Mendel:2014}.

From the NSA catalog's 641,409 galaxies, we find 509 galaxies which are paired to MaNGA targets. MaNGA targets which have both an inside-IFU and an outside-IFU pair are left to the inside-IFU sample. After restricting the sample to SFGs, we have 161 MaNGA targets with paired galaxies outside of the IFU.

We use the r-band elliptical Petrosian apertures from the NSA catalog to describe the geometry of the galaxies in the outside-IFU sample. We also use the stellar masses calculated from the r-band elliptical Petrosian apertures in the NSA catalog for the total stellar mass of the galaxies.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Control Sample}\label{sec:control}
We build a sample of isolated control galaxies from the remaining MaNGA galaxies by selecting the MaNGA target galaxies which have no spectroscopic companions within r$_p$ $<$ 50 kpc and $\Delta$v $<$ 500 km s$^{-1}$ either inside or outside of the IFU. This gives us a set of 1862 SFGs and 1598 SFGs which are covered by both \simard\ and \citet{Mendel:2014}.

The SFR in galaxies has been shown to be dependent on both stellar mass and redshift of the galaxies \citep{Noeske:2007}. This effect needs to be controlled for when comparing the paired and control galaxies to isolate the changes in the sSFR due to merger induced effects. For each galaxy pair we will build a subset of 20 control galaxies which are matched on stellar mass and redshift.

To control for stellar mass, we set a 0.1 dex stellar mass cut between a paired galaxy and the potential control galaxies. To restrict the redshift between the control and paired galaxies, we select control galaxies which are drawn from the same MaNGA subsample (e.g. Primary or Secondary) as the paired galaxy. The MaNGA sample has a tight ``banana" shaped distribution in stellar mass and redshift, seen in Figure \ref{fig:Mi-z}. By setting a 0.1 dex stellar mass cut and requiring that the galaxies be in the same MaNGA subsample, we effectively set a z $\le$ $\sim$0.025 redshift cut. We note that the MaNGA galaxies with stellar masses above \logm\ $\ge$ 11.0 have a wide redshift distribution. In this work, we focus on the galaxies below that mass range.

Setting the above requirements, most paired galaxies will find between 20$-$100 control galaxies. Since we want each paired galaxy to be treated in a similar manner, we will downselect the total number of acquired control galaxies down to 20 controls. We select the 20 controls using a random number generator. In the cases where a paired galaxy does not initially acquire 20 control galaxies we iteratively expand the stellar mass limit by 0.1 dex until at least 20 control galaxies are found.

The control galaxies have their radial profiles of sSFR made with both the r-band elliptical Petrosian apertures from the NSA catalog and the r-band elliptical S\'ersic apertures from \simard. We use the geometries and stellar masses from \simard\ and \citet{Mendel:2014} when the controls are being matched to pairs in the inside-IFU sample and we use the geometries and stellar masses from the NSA catalog when the controls are being matched to pairs in the outside-IFU sample.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Radial Profiles}\label{sec:radial}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=\linewidth]{fig/8083-12703.pdf}
\caption[Example of the difference profiles for the mass-redshift selected control sample.]{The process for building the tailored control sample. The Left panel shows the paired galaxy's profile for sSFR. The Middle panel shows the profiles for sSFR for the selected 20 control galaxies in gray. The red profile is the median profile of the 20 control galaxies where the highlighted region about the profile is the standard error of the mean. The Right panel shows the difference between pair's profile and the stacked control profile.}
\label{fig:dex}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

In order to spatially characterize the star formation in the paired galaxies we build radial profiles of sSFR. As mentioned in Sections \ref{sec:pair} and \ref{sec:control} we use the r-band elliptical Petrosian apertures from the NSA catalog and the r-band S\'ersic apertures from \simard\ to define the geometries of the galaxies. We calculate the inclination angle, {\it i}, of the galaxies using the major-to-minor axis ratios from the elliptical apertures;

@@

The inclination angle, along with the galaxy's position angle, is used to deproject the geometries of the galaxies. The distance to each of the spaxels from the center of the MaNGA target is calculated using the 50\% half light radius to scale the size of the galaxy. The r-band elliptical S\'ersic apertures from \simard\ are used for the inside-IFU sample and their controls and the r-band elliptical Petrosian apertures from the NSA catalog are used for the outside-IFU sample and their controls.

The spaxels are binned into radius increments of 0.1 \reff\ from 0.0$-$2.5 \reff. Within each radius bin we take the median of the specific star formation rate. The profiles' errors are the standard error of the mean of the data within each radius bin. We create one of these individual averaged radial profiles for every MaNGA galaxy.

We use our catalog of photometric objects and the \simard\ catalog to mask foregournd/background objects which may contaminate the data. Objects in our photometric catalog are masked out with a 2\arcsec\ circular aperture and the galaxies from \simard\ are masked out with a 2.0 \reff\ elliptical aperture, using the r-band S\'ersic apertures from the catalog.

We then construct difference profiles between the paired galaxies and the control galaxies. As mentioned in Section \ref{sec:control}, a paired galaxy is matched to 20 similar control galaxies. We take the individual averaged profiles of the control galaxies and take the median value of the profiles at each radius bin giving us a ``stacked" profile of control galaxies. The error of the profile is the standard error of the mean of the individual profiles. We also take into account the error associated with the random selection of controls using a bootstrapping method to quantify the variation in the values of stacked profile over 1000 iterations. This random selection contributes an error of about 0.1 dex.

Once the stacked profile of the control galaxies is made, we take the difference between the paired galaxy's profile and the stacked control profile in log space (this means that the profiles really represents a ratio between the pairs and controls in linear space). An example of the construction of a difference profile is shown in Figure \ref{fig:dex}. We do this process for each of the 202 paired galaxies.

The difference profiles at this stage have now been controlled for stellar mass, redshift, and galaxy size so we can freely stack these profiles to study the global properties of the merging galaxies. We take all of the $\Delta$log(sSFR) profiles and take the median within each radius bin to create a stacked profile which represents the whole pair sample, shown in Figure \ref{fig:ssfr_all}. We can also split the pair sample along different parameters; stellar mass, mass ratio, and projected separation to study how these profiles behave as a function of these parameters, shown in Figure \ref{fig:ssfr_full}. The results of the profiles will discussed in detail in Section \ref{sec:results}.

>>>>

\begin{abstract}
We study the spatial profile of the star formation rate (SFR) in a sample of 160 interacting galaxies within the MaNGA (Mapping Nearby Galaxies at Apache Point Observatory) survey. We find that the specific star formation rate (sSFR) is centrally enhanced in interacting galaxies by $\sim$0.25 $\pm$ 0.1 but that there is no enhancement or suppression in their disks. We find that the level of the central enhancement is independent of galaxy mass. Low mass galaxies experience the same level of enhancement to their star formation rate as high mass galaxies. Assuming a constant burst merger induced star formation over a 1 Gyr period, the mass growth rate in the centers of the paired galaxies will be 1.6$-$2.3$\times$ higher than secular mass growth. Since the merger induced sSFR enhancement is constant over stellar mass, low mass galaxies will experience a higher fractional mass growth rate which is $\sim$4.3 higher than that of high mass galaxies. This indicates that merger induced star formation has a significant impact on the mass evolution of low mass galaxies.

\end{abstract}

\keywords{galaxies: star formation --- galaxies: nuclei --- galaxies: interactions --- galaxies: mass evolution}

@@

% Organization
This paper is organized as follows; in Section \ref{sec:data} we will discuss the properties of the MaNGA survey along with the construction of our pair and control samples, in Section \ref{sec:analysis} we will discuss how we measure star formation rates and how we build radial profiles of star formation, in Section \ref{sec:results} we discuss the results of the constructed radial profiles, and in Section \ref{sec:sum} we discuss and summarize the findings of the work.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Data and Sample}\label{sec:data}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering
\includegraphics[width=\linewidth]{fig/color-mag.pdf}
\caption[]{Color-magnitude diagram for MaNGA galaxies ({\it colored circles}). The color of the symbol reflects the local density around each data point in this color-magnitude plane, as indicated by the color bar on the top. The MaNGA galaxies with close companions are marked with {\it grey diamonds}. From top to bottom, the dashed lines divide the sample into red sequence, green valley, and blue cloud. The star-forming galaxy sample used in this paper are the galaxies below the lower dividing line.}
\label{fig:cmd}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

MaNGA is an a IFS survey based at Apache Point Observatory (APO) which used the SDSS (Sloan Digital Sky Survey) 2.5-meter telescope along with two dual-channel BOSS spectrographs \citep{Drory:2015}. MaNGA captures spectra through 17 integral field units (IFUs) with variable numbers of fibers; 19, 37, 61, 91, and 127 fibers covering 12.5\arcsec, 17.5\arcsec, 22.5\arcsec, 27.5\arcsec, and 32.5\arcsec on the sky respectively \citet{Law:2015}. MaNGA is an optical survey with a spectral coverage of 3600$-$10,300 \AA\ with a resolution of R $\sim$ 2000 and a median spectra coverage of 2.5\arcsec\ FWHM \citep{Bundy:2015}.

The MaNGA survey targets galaxies from a subset of 41,154 galaxies from the NASA-Sloan Atlas (NSA) with a redshift range of 0.01 $<$ z $<$ 0.15 and a luminosity range of -17.7 $<$ $\mathcal{M_{\rm i}}$ $<$ -24.0, where $\mathcal{M_{\rm i}}$ is the rest frame i-band magnitude within the survey's elliptical Petrosian apertures. MaNGA plans to cover 10,000 galaxies with a flat stellar mass distribution at two spatial coverages, 1.5 \reff\ and 2.5 \reff\ (where \reff\ is the radius which contains 50\% of the galaxy's total light). In this work we use the data from the internal data release, MPL-8, which covers 6142 unique galaxies.

We classify galaxies in this survey as star forming galaxies using the color-magnitude diagram (CMD). We show the CMD for the MaNGA survey and our pair sample in Figure \ref{fig:cmd} along with demarcation lines which separate the blue cloud, red sequence, and green valley. We established the demarcation lines by collapsing the CMD to a color histogram for each of the three regions. We then varied the slopes between the regions until we found the slopes which best fit the data. These demarcation lines are;

@@

After the star formation cuts, we require that all galaxies are in the Primary or Secondary MaNGA subsamples \citep{Wake:2017}. We also set a stellar mass range of \logm\ $=$ 9.0$-$11.0.

We build two different pair samples in this work; the inside-IFU sample which contains paired galaxies where both galaxies are covered by a single MaNGA IFU and the outside-IFU sample where a MaNGA target galaxy is coupled with another galaxies found outside of its MaNGA IFU.

\subsection{Inside-IFU Sample}\label{sec:inside}

In our previous work, \citet{Fu:2018}, we showed that $\sim$5.7\% of the MaNGA observations have at least one companion galaxy within the field of view of the IFU. In this work we use a refined pair identification process which is also expanded for the most recent internal data release, MPL-8.

We use SDSS photometric objects to create a catalog of objects within the fields of view of the MaNGA IFUs. We extract their spectra from the MaNGA datacubes through a 1\arcsec\ aperture and fit the spectra with {\sc SPFIT} assuming the MaNGA target's redshift. The spectra is then sorted into different categories; ``good" galaxy spectra, broad-line AGN (active galactic nuclei), foreground star, foreground/background galaxies, or poor S/N objects. The ``good" galaxy spectra are the objects whose spectra is well modeled by {\sc SPFIT} at the target galaxy's redshift, whether it is the target galaxy itself or a nearby companion galaxy. This means that the companion galaxy can be within $\pm$3000 km s$^{-1}$ of the MaNGA target. We found 6573 ``good" objects, 57 broad-line AGN, 836 foreground stars, 319 foreground/background galaxies, and 1546 objects with poor S/N.

From the 6573 galaxies with good spectra, 404 of the MaNGA IFUs have multiple objects within the IFU. We further restrict the sample by setting a relative velocity cut of $\Delta$v $<$ 500 km s$^{-1}$ to remove projected companions and we also require that the galaxies are classified as star forming by the CMD diagram. These requirements reduce our sample down to 124 star forming galaxies (SFGs).

We characterize the geometry of the inside-IFU galaxies with the r-band elliptical S\'ersic apertures from \citet{Simard:2011} and we characterize the total stellar mass of the galaxies with the stellar masses from \citet{Mendel:2014}. We use \citet{Simard:2011} instead of the apertures from the NSA catalog, which the MaNGA sample is drawn from, because the apertures in the NSA catalog often fail to fit the MaNGA galaxies when there is another nearby, bright object.

The \citet{Simard:2011} and \citet{Mendel:2014} catalogs do not completely cover the MaNGA sample. Out of the 124 SFGs in the inside-IFU sample, 33 of the SFGs are covered by both \citet{Simard:2011} and \citet{Mendel:2014}.

From the NSA catalog's 641,409 galaxies, we find 361 galaxies which are paired to MaNGA targets. MaNGA targets which have both an inside-IFU and an outside-IFU pair are left to the inside-IFU sample. After restricting the sample to SFGs, we have 127 MaNGA targets with paired galaxies outside of the IFU.

We use the r-band elliptical Petrosian apertures from the NSA catalog to describe the geometry of the galaxies in the outside-IFU sample. For cases where the identified galaxy pair is outside of the MaNGA IFU, the NSA catalog's algorithm is able to fit the MaNGA target's geometry well. We also use the stellar masses calculated from the r-band elliptical Petrosian apertures in the NSA catalog for the total stellar mass of the galaxies.

\subsection{Control Sample}\label{sec:control}
We build a sample of isolated control galaxies from the remaining MaNGA galaxies by selecting the MaNGA target galaxies which have no spectroscopic companions within r$_p$ $<$ 50 kpc and $\Delta$v $<$ 500 km s$^{-1}$ either inside or outside of the IFU. This gives us a set of 1891 SFGs and 1528 SFGs which are covered by both \citet{Simard:2011} and \citet{Mendel:2014}.

The SFR in galaxies has been shown to be dependent on both stellar mass and redshift of the galaxies \citep{Noeske:2007}. This effect needs to be controlled for when comparing the paired and control galaxies to isolate the changes in the sSFR due to merger induced effects. For each galaxy pair we build a subset of 20 control galaxies which are matched in stellar mass and redshift.

To control for stellar mass, we set a 0.1 dex stellar mass limit between a paired galaxy and the potential control galaxies. To restrict the redshift between the control and paired galaxies, we select control galaxies which are drawn from the same MaNGA subsample (e.g. Primary or Secondary) as the paired galaxy. The MaNGA sample has a tight ``banana" shaped distribution in stellar mass and redshift. By setting a 0.1 dex stellar mass cut and requiring that the galaxies be in the same MaNGA subsample, we effectively set a z $\le$ $\sim$0.025 redshift cut. We note that the MaNGA galaxies with stellar masses above \logm\ $\ge$ 11.0 have a wide redshift distribution, our galaxy samples are restricted to a stellar mass range between \logm\ $=$ 9.0$-$11.0.

Setting the above requirements, most paired galaxies will find between 20$-$100 control galaxies. Since we want each paired galaxy to be treated in a similar manner, we will downselect the total number of acquired control galaxies down to 20 controls using a random number generator. In the cases where a paired galaxy does not initially acquire 20 control galaxies we iteratively expand the stellar mass limit by 0.1 dex until at least 20 control galaxies are found.

The control galaxies have their radial profiles of sSFR made with both the r-band elliptical Petrosian apertures from the NSA catalog and the r-band elliptical S\'ersic apertures from \citet{Simard:2011}. We use the geometries and stellar masses from \citet{Simard:2011} and \citet{Mendel:2014} when the controls are being matched to pairs in the inside-IFU sample and we use the geometries and stellar masses from the NSA catalog when the controls are being matched to pairs in the outside-IFU sample.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Radial Profiles of Star Formation}\label{sec:analysis}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering
\includegraphics[width=\linewidth]{fig/bpt_spax.pdf}
\caption[]{The 2-D histogram showing the BPT classification \citep{Baldwin:1981} of individual spaxels within our star-forming control and pair samples. The color of each bin represents the number density of spaxels, normalized to one. The solid black line represents the theoretically determined maximum starburst line of \citet{Kewley:2001} and the dashed black line is the analytical \citet{Kauffmann:2003} line.}
\label{fig:bpt}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Emission Line Extraction}

%%% Reddening
We correct the emission lines for reddening using the extinction curve from \citet{Cardelli:1989} with updated coefficients from \citet{ODonnell:1994}. The extinction in parameterized as R$_V$ $\equiv$ A$_V$/E(B$-$V) $=$ 3.1, where we estimate the value of the V-band extinction, A$_V$, by comparing the H$\alpha$/H$\beta$ ratio to the expected value of 2.85 for case-B recombination. The extinction correction is applied to all of the extracted emission lines.

\subsection{Star Formation Rate}

@@

Since the stellar mass of a galaxy is not uniformly distributed within the galaxy, we normalize the SFR by the local stellar mass, giving us the specific star formation rate (sSFR). The local stellar masses used here is the stellar mass calculated by {\sc SPFIT}'s fit to the stellar continuum within each spaxel (spatial pixel).

@@

We use the BPT diagnostic \citep{Baldwin:1981} to remove spaxels which were not ionized by star formation. Ionization sources are often separated by either the theoretical maximum starburst line from \citet{Kewley:2001} or the analytically fitted line from \citet{Kauffmann:2003}, given below in Equations \ref{eq:kewley} and \ref{eq:kauffmann} respectively.

Where \OIII$\lambda$5007, H$\beta$, \NII$\lambda$6584, and H$\alpha$ are emission line fluxes within each MaNGA spaxel. We depict the BPT diagram for each spaxel in the MaNGA survey in Figure \ref{fig:bpt} along with the demarcations for star formation from \citet{Kewley:2001} and \citet{Kauffmann:2003}. We use the \citet{Kewley:2001} demarcation line as the limit for classifying star formation in the MaNGA spaxels.

It has also been shown that hot low mass evolved stars (HOLMES) in retired galaxies can mimic HII regions and AGN on the BPT diagram \citep{Stasinska:2008}. We apply an H$\alpha$ equivalent width (EW) cut of \ewha\ $>$ 3\AA\ to mask retired spaxels \citet{Cid-Fernandes:2011}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Geometry}\label{sec:radial}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=\linewidth]{fig/ssfr_comb.pdf}
\caption[]{The log(sSFR) as a function of galactocentric radius for control galaxies (\textbf{Left}) and galaxy pairs (\textbf{Middle}). The difference between the profiles of the paired galaxies and the control galaxies are shown in the \textbf{Right} panel. The dashed black profile represents the mean of the difference profiles). The colors of the profiles represent the mass range of the selected galaxies and the highlighted region around the profiles represent the standard error of the mean of the data at the given radius interval.}
\label{fig:ssfr_prof}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

In order to spatially characterize the star formation in the paired galaxies we build radial profiles of sSFR. As mentioned in Section \ref{sec:data} we use the r-band elliptical Petrosian apertures from the NSA catalog and the r-band S\'ersic apertures from \citet{Simard:2011} to define the geometries of the galaxies. We calculate the inclination angle, {\it i}, of the galaxies using the major-to-minor axis ratios from the elliptical apertures;

@@

The inclination angle, along with the galaxy's position angle, is used to deproject the geometries of the galaxies. The distance to each of the spaxels from the center of the MaNGA target is calculated using the 50\% half light radius to scale the size of the galaxy. The r-band elliptical S\'ersic apertures from \citet{Simard:2011} are used for the inside-IFU sample and their controls and the r-band elliptical Petrosian apertures from the NSA catalog are used for the outside-IFU sample and their controls.

The spaxels are binned into radius increments of 0.1 R/\reff\ from 0.0$-$2.5 R/\reff. Within each radius bin we take the median of the specific star formation rate. The profiles' errors are the standard error of the mean of the data within each radius bin. We create one of these individual averaged radial profiles for every MaNGA galaxy.

We use our catalog of photometric objects and the \citet{Simard:2011} catalog to mask foregournd/background objects which may contaminate the data. Objects in our photometric catalog are masked out with a 2\arcsec\ circular aperture and the galaxies from \citet{Simard:2011} are masked out with a 2.0 \reff\ elliptical aperture, using the r-band S\'ersic apertures from the catalog.

With individual log(sSFR) profiles built for each MaNGA galaxy, we now use two different methods to compare the profiles of paired galaxies against the profiles of control galaxies. The first method, in Section \ref{sec:mass-bin}, paired galaxies are compared to control galaxies within evenly spaced stellar mass-bins. In the second method, in Section \ref{sec:tailored}, paired galaxies are compared to a subset 20 control galaxies which have a similar stellar mass and redshift.

\subsection{Mass-Binned Difference Profiles}\label{sec:mass-bin}

In the first method, paired and control galaxies are grouped into four evenly spaced stellar mass bins between \logm\ $=$ 9.0$-$11.0. Within each stellar mass bin, we create a median profile of log(sSFR) as a function of galactocentric radius for both paired and control galaxies. The control profiles are constructed using all available control galaxies within each mass bin. The error associated with the profile is the standard error of mean of the data at each radius bin. We show these ``stacked" profiles for control galaxies in the left hand panel of Figure \ref{fig:ssfr_prof} and the stacked profiles for paired galaxies in the middle panel of Figure \ref{fig:ssfr_prof}.

Once the stacked profiles are made, we take the difference between the stacked profiles of the paired galaxies and the control galaxies, pair - control, in log space (this means that the profiles really represents a ratio between the pairs and controls in linear space). This gives us difference profile, $\Delta$log(sSFR), which shows us where the sSFR is enhanced or suppressed (shown in the right hand panel of Figure \ref{fig:ssfr_prof}). We will discuss the results of the difference profiles later in Section \ref{sec:results}.

\subsection{Tailored-Controls Difference Profiles}\label{sec:tailored}
